On the presentation of orthogonal groups over polynomial rings

### 2019-05-02 dl-paper.tex
Minor fix

\begin{corollary} \label{Kgen-strong}
 For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\St(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(f, \eta)$, $f \in M[X]$, $\eta \in XA[X]$.
\end{corollary}
\begin{proof}
 Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$ belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$. Similar argument also works for the negative roots. The required assertion now follows from the above proposition.
\end{proof}

@@

It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
Substituting in~\eqref{Z5} of~\cref{Crels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2), \end{multline}
where $\epsilon = N_{\alpha,\beta}$.  
The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}

>>>>

\begin{corollary} \label{Kgen-strong}
 For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma\in \Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\St(\Phi, A[X], XM[X])$ and the elements $c_{\pm \gamma}(f, \eta)$, $f \in M[X]$, $\eta \in XA[X]$.
\end{corollary}
\begin{proof}
 Choose some ordering on $\Phi$ with respect to which $\gamma$ becomes the maximal positive root. 
 Invoking~\eqref{C4} of~\cref{Crels} with $I = M[X]$, $J=XA[X]$, $\xi = 1$ we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(f, \eta)$ is equivalent to 
 $c_{\alpha}(-\epsilon f, -\epsilon \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. 
 Arguing by induction on the height of $\alpha$ we conclude that all $c_\alpha(f, \eta)$, $\alpha \in \Phi^+$
 belong to the subgroup generated by $\overline{\St}(\Phi, A[X], XA[X])$ and $c_\gamma(f, \eta)$.
 Similar argument also works for the negative roots, and the required assertion now follows.
\end{proof}

@@

It remains to verify the assertion for the remaining generator $z_\alpha(f, X\xi)$ of type 2.
Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon \xi$, $\eta=X$ and expressing $z_\alpha(f, X\xi)$ through other terms we obtain that
\begin{multline} \nonumber z_\alpha(f, X\xi) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-X^2 f \xi) \cdot x_{-\beta}(f \xi) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon \xi) \cdot z_{-\beta}(-f\xi, -X) \cdot x_{-\alpha-\beta}(-\epsilon X f \xi^2) \cdot x_{-\alpha}(-X^2 f\xi^2), \end{multline}
where $\epsilon = N_{\alpha,\beta}$.  
The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. 
It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, 
while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. \end{proof}
